[dcpo_demsupport] Appendix

### 2020-07-15 paper/dcpo_demsupport_appendix.Rmd
clean up

vcovBK_se <- function(x){
  vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()}

@@

summary(result_m5O)
summary(mitools::MIcombine(results = result_betas_m5, 
                           variance = result_vars_m5))
```

>>>>

vcovBK_se <- function(x) {
  vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

@@

summary(result_m5O)
summary(mitools::MIcombine(results = result_betas_m5, 
                           variance = result_vars_m5))

first_year <- min(claassen_replication_input$data$year)

df_theta <- purrr::map(1:1000, function(x) {
  claassen_m5_theta$theta[x,,] %>% 
    as_tibble() %>% 
    rename_with(~ls_country, .cols = starts_with("V")) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = ls_country,
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(df_controls, by = c("country" = "Country", "year" = "Year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_m5_1k <- map(df_theta, function(aDataset) {
  plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(theta, 1) + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1), model="pooling", data = aDataset)
})

result_betas_m5_1k <- mitools::MIextract(result_m5N_1k, fun = coef)
result_vars_m5_1k <- mitools::MIextract(result_m5N_1k, fun = vcovBK_se)

summary(mitools::MIcombine(results = result_betas_m5_1k, 
                           variance = result_vars_m5_1k))
```
